Privacy-Respecting Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
sec 3

We added a telemetry subsystem to Roblox Studio in order to study type errors
in Luau code.
This section explains the constraints our telemetry had to meet~(\cref{s:tel-limitations})
and the final design~(\cref{s:telemetry-records}).

@@

The type error telemetry for a Roblox Studio session is gathered as a series of
records, all with the same \panon{} session identifier.
This allows us to correlate telemetry across a single
session, but not between sessions.
In order to avoid swamping the telemetry servers, the client reports on a subset
of telemetry events via two levels of uniform random sampling:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions generate \emph{any} type error telemetry, and
  \item
    0.5\% of all type analyses (approximately 1 in 200 keystrokes)
    in an enrolled session generate a telemetry record.
\end{itemize}
In addition to sending telemetry for randomly-selected keystrokes,
our system sends a telemetry record every time the session changes
focus from one module to another.
These records provide important context for mode switches:
if one record uses \mstrict{} mode but the next uses \mnocheck{},
then it is critical to know whether the creator downgraded modes
or simply switched to another module.

>>>>

We added a subsystem to Roblox Studio's telemetry in order to study type errors
in Luau code.
This section explains the constraints our telemetry had to meet~(\cref{s:tel-limitations})
and the final design~(\cref{s:telemetry-records}).

@@

The type error telemetry for a Roblox Studio session is gathered as a series of
records, all with the same per-session \panon{} session identifier.
This allows us to correlate telemetry across a single
session, but not between sessions.
In order to avoid swamping the telemetry servers, the client reports on a subset
of telemetry events via two levels of uniform random sampling:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions generate \emph{any} type error telemetry, and
  \item
    0.5\% of all type analyses (approximately 1 in 200 keystrokes)
    in an enrolled session generate a telemetry record.
\end{itemize}
In addition to sending telemetry for randomly-selected keystrokes,
our system sends a telemetry record every time the session changes
focus from one module to another.
These records provide important context for mode switches:
if one record uses \mstrict{} mode but the next uses \mnocheck{},
then it is critical to know whether the creator downgraded modes
or simply switched to another module.
